# Ex 1- Part C 

## Part 1  

installation of R and Rstudio!  

## Part 2

### Question 1
```{r}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

* the penguins table contains measurements data for 344 penguins, from 3 different islands according to 8 different attributes as described in the columns:  
the columns descirbe the attributes(labels) of the penguins:  
    * species 
    * island 
    * bill leangth in mm 
    * bill depth in mm 
    * flipper length in mm 
    * body masss in grams 
    * sex 
    * year  

fct=categorial variable ; species,island and sex.  
dbl=numeric variable ; bill depth in mm.  
int=integer variable ; flipper length in mm,body mass in grams and year.  

the rows describe the values of the attributes - each row represents the data of one penguin in the study.

### Question 2
```{r}
head(penguins)
tail(penguins)
View(penguins)
penguins
```

#### a.
a.1  
[view](https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/View) - Invoke a spreadsheet-style data viewer on a matrix-like R object.  
a.2  
[head](https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/head)- Returns the first or last parts (depends on the `n` argument) of a vector, matrix, table, data frame or function. the default will return the first 6 rows.  
a.3  
[tail](https://www.rdocumentation.org/packages/rotations/versions/1.6.1/topics/tail) - Returns the first or last parts (depends on the `n` argument) of a vector, matrix, table, data frame or function. the default will return the last 6 rows.  
a.4  
[glimpse](https://www.rdocumentation.org/packages/dplyr/versions/0.3/topics/glimpse)- Get a glimpse of your data. (This is like a transposed version of print: columns run down the page, and data runs across. This makes it possible to see every column in a data frame ).    
a.5  
writing `penguins` in the console will show the whole penguin's table in the console view.

#### b.
b.1  
every row in the table describes the values of the corresponding attribute for the sampled penguin.  
b.2  
island variable describes the location from which the samples penguin has came from.
b.3  
species variable describes the breed of the samples penguin.  

### Question 3    
>`%>% is called the forward pipe operator in R. It provides a mechanism for chaining commands with a new forward-pipe operator, %>%. This operator will forward a value, or the result of an expression, into the next function call/expression.`
>[count](https://www.rdocumentation.org/packages/dplyr/versions/0.3/topics/count) - Count the number of rows in each group.  
```{r}
penguins %>%
count(island)
penguins %>%
count(sex)
```

#### a.  
a.1  
number of islands in the data - **3** .  
a.2  
male penguins- **168**.  
a.3  
observations of penguins that lack information about sex- **11**.
   
## Part 3  
```{r}
ggplot(data = penguins,
aes(x = bill_length_mm,
y = flipper_length_mm,
color = species)) +

geom_point()
```

#### a  
a.1  
the meaning of the warning message is that there are two rows in the data that are missing the values for bill_length_mm or flipper_length_mm - they are represented in the data as NA and thus removed from the plot.  
(if the axes are set manually and the data falls out of range the warning message will appear accordingly).   
the ggplot funciton automaticlly removes them from the plot due to lack of data.

we can find the above rows as such:  
```{r}
which(is.na(
    penguins[, c("flipper_length_mm", "bill_length_mm")]),
    arr.ind = TRUE)
```
> we can see that the rows with the missing values are: 4 and 272.  

a.2  

the plot shows the relation between the bill_length_mm and the flipper_length_mm for each species.  
we can conclude from the location of the plots and colors that their is a correlation between the flipper length and the beak(bill) length -  
the longer the flipper is thus the longer the beak is.  
more over, we can see that the `Gentoo` penguins have the most elongated flipper and bill and the `Adelle` and `Chinstrap` have approximly the same flipper length but the `Chinstrap` has a longer bill.  

a.3 

* [aes](https://www.rdocumentation.org/packages/ggplot2/versions/3.3.5/topics/aes) - Aesthetic mappings describe how variables in the data are mapped to visual properties (aesthetics) of geoms. Aesthetic mappings can be set in ggplot() and in individual layers.  
* [ggplot](https://www.rdocumentation.org/packages/ggplot2/versions/3.3.5/topics/ggplot) - initializes a ggplot object. It can be used to declare the input data frame for a graphic and to specify the set of plot aesthetics intended to be common throughout all subsequent layers unless specifically overridden.  
* [geom_point](https://www.rdocumentation.org/packages/ggplot2/versions/3.3.5/topics/geom_point) - The point geom is used to create scatterplots.  

a.4  

```{r}
ggplot(data = penguins,
aes(x = bill_length_mm,
y = bill_depth_mm,
color = island)) +

geom_point()
```  

a.5  
The graph describes the relation between bill size (depth and length) and the island in which the penguin live.
It can be seen that most of the penguins from `Torgersen` island have shorter bill length and longer bill depth compared to others.
Furthermore, The measurements of penguin's bill from other islands are more dispersed (bigger variance) than in `Torgersen` island.   
[It is known that penguins with a long and thin bill are fish eaters and the ones with the short and wide bill are krill eaters](https://seaworld.org/animals/all-about/penguins/physical-characteristics/),  
so we can assume according to the plot, that the pengnuins in `Biscoe` island are mostly fish eaters , the penguin in and `Dream` island are mostly krill eaters and the penguins in `Torgersen` are krill eaters.
  
More over it is possible that in `Dream` and `Torgerse` islands the penguins are of different species thus have different bill sizes.
Also We should take into consideration that differences among islands could be accounted for by variables like sex; in some species the male penguin has longer bill than the female. with that said the distribution of male vs female also effects greatly on the plot. 

